**The Role of Interoception and Theory of Mind in Deception**

### 2022-08-31 paper/manuscript_v0.Rmd

To measure interoception, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart], where participants count their heart beats without taking their pulse, as well as provide a confidence rating for their estimate. At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy. They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated statements such as "I can use my breath to reduce tension" on a Likert scale.

Heartbeat Tracking Task (HTT) - tap one

@@

LIE Scale ???? - doms scale structure of deception

>>>>

To measure interoception, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart], where participants count their heart beats without taking their pulse, as well as provide a confidence rating for their estimate. At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy. They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated 32 statements such as "I can use my breath to reduce tension" on a 1-5 Likert scale.

Additionally, we implemented the Heartbeat Tracking Task (HTT), in which participants  - tap one

@@

We used the *LIE Scale*, which is a 44-item questionnaire examining deception as a dispositional trait, and measures the participant propensity towards lie frequency, ability, contextuality and negativity [@makowski2021structure]. (!CHECK!)
